### 2017-01-03 paper/paris17/paper.tex
Yi Shen revise it

The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation. However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time, which is impractical for real seismic modeling in terms of memory capacities on modern computers. Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave,shen2015image}. However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.

@@

Our theory is built on the foundation of \cite{zhu2014theory}. The time-domain differential equation is based on the Laplacian differential operators of fractional order, which is able to model seismic wave propagation in constant-Q viscoelastic media. The stress-strain relation is derived from the classical equation expressed in terms of fractional time derivatives. The formulation has the advantage of not requiring additional field variables so that it saves the computing time and storage significantly \cite[]{zhu2014theory}.

We extend the formulation of \cite{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case. Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities. Also, we further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared with the attenuation of the signals. As a result, our equations are as follows.

>>>>

The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation. However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time, which is impractical for real seismic modeling in terms of memory capacities on modern computers. Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave}. However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.

@@

Our theory is built on the foundation of \cite{zhu2014theory}. The time-domain differential equation is based on the Laplacian differential operators of fractional order, which is able to model seismic wave propagation in constant-Q viscoelastic media. The stress-strain relation is derived from the classical equation expressed in terms of fractional time derivatives. The formulation has the advantage of not requiring additional field variables so that it saves the computing time and storage significantly.

We extend the formulation of \cite{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case. Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which not only significantly reduces the computing complexities but also preserves the accuracy if Q is not extremely low \cite[]{shen2015image}. We further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared with the attenuation of the signals. As a result, our equations are as follows.
